---
title: "Code_Book"
author: "SFP"
date: "7/5/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

The run_analysis.R file takes data saved on local drive from the assignment website, merges train and test data, labels it, and creates a separate data set with the means by activity of all variables related to measurement means and standard deviation.

To do so, I column bound the X and Y sets for both train and test data, the row bound the resulting two datasets into one. Having downloaded the features list, I replaced the column names with the feature names. Then I used grep() to extract mean and standard deviation measure. Then I merged the data set with the activity labels so I could then replace the numbers of the activities with their respective labels. After, I used group_by() and summarise_all() to calculate mean of each column by activity.  
```{r}
setwd("~/R/Coursera/Cleaning data/getdata_projectfiles_UCI HAR Dataset/UCI HAR Dataset")
features<-read.table('features.txt', header = FALSE)
meancols<-grep("mean()",features$V2)
stdcols<-grep("std()",features$V2)
#Join indices into one object
datacols<-c(meancols,stdcols)
variables<-features[datacols]
print(variables)
```
The variables above correspond to each of the mean and standard deviation measures from the device and their corresponding mean by activity. 